Evaluation of performances

### 2020-03-05 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

>>>>

Fold performances of "SVM MBO No Filter" on the HR Task

- Fold 1: Luiando
- Fold 2: Laukiz1
- Fold 3: Laukiz2
- Fold 4: Oiartzun

```{r}
df <- mlr::getBMRPerformances(bm_aggregated_new_buffer2,
  "hr_buffer2", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Laukiz1 = "2", Laukiz2 = "3",
    Luiando = "1", Oiartzun = "4"
  )) %>% 
  dplyr::mutate(RMSE = round(RMSE, 2))

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Single fold performances for learner SVM on the HR dataset without using a filter.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/ieee/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(df_tab, here("docs/00-manuscripts/presentation/table-svm-single-plot.rda"))

flextable::flextable(df_tab)
```
